Whole Genome Resequencing for Population Genomics

### 2022-01-20 WGS_intro.Rmd
added authors
Added bibtex refs

---
bibliography: RCN_site-Nov05.bib
title:  Whole Genome Resequencing for Population Genomics 
---

@@

However, the line between high-to-moderate-coverage WGS and low-coverage WGS is not always as clear-cut as presented above. For example, with moderate-coverage WGS (e.g. 5-20x), many sites within an individual can still have low coverage due to random sampling, resulting in unreliable genotype calls and/or missing data that can become problematic in downstream analysis. Therefore, it could be preferrable to avoid hard-calling genotypes with moderate-coverage WGS in certain applications. On the other hand, in populations with high levels of linkage disequilibrium (LD), it could be possible to leverage LD to carry out genotype imputation, making genotype calling a lot more accurate with low-coverage WGS data. Imputation is more likely to be successful when a high-quality reference panel exists in the system ([Fuller et al. 2020](https://www.science.org/doi/10.1126/science.aba4674), [Rubinacci et al. 2021](https://www.nature.com/articles/s41588-020-00756-0)), but methods for imputation without such reference panels have also been developed (in which case a very large sample size would be required, [Davis et al. 2016](https://www.nature.com/articles/ng.3594)).

>>>>

---
bibliography: RCN_site-Nov05.bib
title:  Whole Genome Resequencing for Population Genomics 
subtitle: '*Katherine Silliman, Nicolas Lou*'
---

@@

However, the line between high-to-moderate-coverage WGS and low-coverage WGS is not always as clear-cut as presented above. For example, with moderate-coverage WGS (e.g. 5-20x), many sites within an individual can still have low coverage due to random sampling, resulting in unreliable genotype calls and/or missing data that can become problematic in downstream analysis. Therefore, it could be preferrable to avoid hard-calling genotypes with moderate-coverage WGS in certain applications. On the other hand, in populations with high levels of linkage disequilibrium (LD), it could be possible to leverage LD to carry out genotype imputation, making genotype calling a lot more accurate with low-coverage WGS data. Imputation is more likely to be successful when a high-quality reference panel exists in the system ([@Fuller2020](https://www.science.org/doi/10.1126/science.aba4674), [@Rubinacci2021-dm](https://www.nature.com/articles/s41588-020-00756-0)), but methods for imputation without such reference panels have also been developed (in which case a very large sample size would be required, [@Davies2016-rq](https://www.nature.com/articles/ng.3594)).
